\begin{post}
	\postdata{Time goes by...}{2011}{11}{18}{20}{20}{33}
	\begin{content}
Seriously, is it Friday again? That's serious mess. Time flies so fast, and even though one proverb says that \textit{"Time flies when you have fun"}, I really did not expect it fly that fast.

Not all stuff is that cool, though. Yesterday some mofo \textbf{stole} some money from my wallet in the gym. I forgot it in my pants in an unlocked locker and someone just seized the given opportunity. I lost approx. 150,000 KRW, which is something like €96. Yeah, bummer. Since the locker is in the shower room, there is no CCTV and I really do not remember all the people that went to the gym while I was working out. Well, it's gone now, so there is nothing I can do, except for crying and punching someone in the face. Life does sometimes suck...

Today I've decided to do nothing and hopefully catch up on the slack I have with my blog. There are at least two posts that I have on my mind, but did not get to the writing part. I guess I need some (female) assistant to do that for me.

To give you brief heads up — on Tuesday we went on another field trip, about which I will write later, because it was completely awesome. After that I finally got to see the War Memorial, which almost concludes the list of touristic places in Seoul that I wanted to visit. Yeah, check!

On Wednesday me and Marc paid another visit to "our" tailor in Itaewon, where we had the first fitting of our suits. Yep, I am having a suit done here. I was a little nervous about the color, because I was not sure how it would look on the completed suit. Well, the fitting exceeded my expectations. Despite not being completed, the suit fit me so well. And the color was perfect, too. Damn, I am going to look so hot in that suit! Ladies will go crazy...

Yesterday's night was in the name of \sout{love} clubbing again. Despite all the heroic statements, we ended up being just 4 — Kate, Morgan, Marc and me. At around 11:20pm, after zero pre-gaming, we took a taxi to Hongdae to Club Naked, where the "School Uniform Party Vol. II" was supposed to take place. Frankly, I have not seen a single school uniform that night. What I have seen, though, was a lot of white faces. The club was packed with foreigners, which seriously sucked. A big part of the people in the club were "stylish douchebags" from prestigious French business schools, that behaved like the club was theirs. Damn, I really got unused to the European testosterone fueled club behavior.

After about an hour in the club, we "took" André and went to Cocoon, which was much better, since there were almost no foreigners and we could dance on the stage and be cool. Yea, this is how we rolled.

Tomorrow, we are planning to go see the Lantern Festival in the city center, which is supposed to be pretty, so I'll try to snap some pictures for your viewing pleasure.
	\end{content}
\end{post}
