%!TEX root = soulexchange.tex
\clearpage

I am sorry that there is no closing post, but since I am writing this on December 13th, I still have time to write one next week. Unfortunately, at that time this book will hopefully be in the print shop, so it will be quite impossible to add it there, since I am no Marty McFly.

Anyway, I would like to use this space to thank every body for their attention to my blog and to all the support they provided me during the four months. First of all, I want to thank my parents, because without them, this all would not happen. They always supported my decisions and actions, and I am infinitely grateful for that. They are the bestest!!! Moreover, I want to thank my sister for the idea to publish this book, because I really had fun doing that. I also want to thank the rest of my family for being my family. I can't wait to see you all next week.

From KAIST, I want to thank Jin and Kayla from the international office. They pampered us like babies and really helped us when we had any difficulties. And they went partying with us!

From other exchange students, I would like to thank Marc for everything, Rik for being my roomie and André for proving that not all French people have to have a strong accent in English. Moreover, I want to thanks Karin, Lauriane and Imane for hanging out with us, thus reducing the ``sausage factor'' of our group. I also want to thank Kate for taking me to see the last Twilight, because it was simply unbelievable. I could not believe how bad it was. Finally, I want to thank Florian, Daniel, Niklas, Till, Morgan, Toy, Mateusz, Piotr, Tomasz, Andrei, Eddy, Mario, Simone, Pierre, Eduard, Canna, Ada, Jenny, Yue, Dieter, Alexa and Elaine for being there and making the whole 4 months legendary.

So...

{\hfill\H 안녕하세요}