After these 4 months I can't even believe I was actually deciding whether I should come to Seoul or not. What was I thinking for God's sake. What could possibly be better than spending 4 months in a country where girls wear heels and short skirt all the time, the McDonalds has a delivery service and where tomorrow really means today, because there is a 8 hour time difference.

I am also quite happy that I was able to keep my blog up and running. Even though I did not publish as many posts as, for example, Karin, I think I managed to capture the core of these 4 months from my perspective. Unfortunately some experiences were simply not recordable in words or transferable. So unless you build some device to read my memories, they will stay in my head forever.

This thing you are holding in your hand is, as you surely know, my blog on paper. I took the posts, typeset them using \LaTeX and got them printed and bounded. Well, at least I hope that's what happened and you really are holding it, because as I am writing this introduction, the whole ``book'' still exists only as a bunch of \texttt{tex} files on my computer, and I will send it to the printshop in few days. I kind of feel like in Back to the Future now, because I am writing about things that will happen in the future, but earlier than someone else will read this. Anyway, I have to give credit to my sis for the idea to try to publish my blog. I have to admit I really enjoyed making it, because it allowed me to tinker with \LaTeX and Python and git, which certainly pleased the geeky part of me.

So, to wrap it up, I want to thank everybody I met in Seoul, because it would not be as legendary as it was. I really hope that our plan to attend each other's graduation will work out.