% XeLaTeX can use any Mac OS X font. See the setromanfont command below.
% Input to XeLaTeX is full Unicode, so Unicode characters can be typed directly into the source.

% The next lines tell TeXShop to typeset with xelatex, and to open and save the source with Unicode encoding.

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt,a5paper,landscape,twoside,openright]{memoir}
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}

\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Mapping=tex-text]{Myriad Pro}
\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Gill Sans}
\setmonofont[Scale=MatchLowercase]{Andale Mono}

\title{Brief Article}
\author{The Author}

%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle

\chapter{Introduction}

\chapter{September 2011}

\chapter{October 2011}

\chapter{November 2011}

\chapter{December 2011}

Your bones don't break, mine do. That's clear. Your cells react to bacteria and viruses differently than mine. You don't get sick, I do. That's also clear. But for some reason, you and I react the exact same way to water. We swallow it too fast, we choke. We get some in our lungs, we drown. However unreal it may seem, we are connected, you and I. We're on the same curve, just on opposite ends.

Now that there is the Tec-9, a crappy spray gun from South Miami. This gun is advertised as the most popular gun in American crime. Do you believe that shit? It actually says that in the little book that comes with it: the most popular gun in American crime. Like they're actually proud of that shit. 

Now that there is the Tec-9, a crappy spray gun from South Miami. This gun is advertised as the most popular gun in American crime. Do you believe that shit? It actually says that in the little book that comes with it: the most popular gun in American crime. Like they're actually proud of that shit. 

The path of the righteous man is beset on all sides by the iniquities of the selfish and the tyranny of evil men. Blessed is he who, in the name of charity and good will, shepherds the weak through the valley of darkness, for he is truly his brother's keeper and the finder of lost children. And I will strike down upon thee with great vengeance and furious anger those who would attempt to poison and destroy My brothers. And you will know My name is the Lord when I lay My vengeance upon thee.

\end{document}  