\begin{post}
	\posttitle{안녕하세요}
	\postdate{2011}{9}{8}{23}{45}{41}
	\begin{content}
Writing a diary does not work for me. The longest time I was able to regularly update a diary was about 2 weeks. The problem is not lack of interesting stuff to write down. The problem is either too much stuff to write down or good ol' laziness. Especially the latter, which also causes that there is still no post about my Kenyan adventure, even though those 15 days were überawesome. Anyway, here I will try to write down some interesting points about my 4 months in Seoul, South Korea. Btw. I have no idea what "soul exchange" could possibly mean, I just liked the joke in it. And if you don't consider it funny...

<h3>28.8.</h3>

<ul>

	<li>Emirates cabin crew's portfolio of languages is very impressive</li>

	<li>The last Pirates of Carribean are boring. On the other hand, The Best Movie Ever Sold is hilarious.</li>

	<li>Dubai Airport is boring. Everything is supersized and full of bling. And there is not enough space to sit down. Seriously, people, 30 seats at the gate are not enough for a flight that is operated by 500+ Airbus A380. However, the airport is quite cheap. A McD menu is 24 of their funnymoney (United Arab Emirates Dirham, to be precise), which is around 4,60 Euros. And you don't have to pay extra for ketchup.</li>

	<li>Airbus A380 is H-U-G-E! It's like a A320 after three years on steroids. And the ICE on-board entertainment system is supercool. They did not have Fight Club or Bring Me The Horizon on it, though.</li>

	<li>Incheon airport has a cool train between the terminal and main building.</li>

	<li>It was supercool that my mentor picked me up at the airport. I was just a little disappointed that he did not have a big sign with my name:)</li>

	<li>Seoul is less dense than I expected. It perfectly fulfills the idea of an Asian supercity, though.</li>

	<li>Kia, Hyundai, Kia, Daewoo, Hyundai, Samsung (!), Kia, Ssangyong, Chinese Mercedes rip-off, that's how the streets look like. Ah, there is one BMW, nice. The import tax on non-Korean cars is so high that people can't afford them (I heard).</li>

	<li>I think I might be a little too old for a shared room in a dorm, where toilets and showers are shared with another 10 people. Makes me miss my spacebox...</li>

	<li>Korean TV shows are just insane!</li>

</ul>

<h3>29.8.</h3>

<ul>

	<li>Cold noodles for lunch. Seriously?</li>

	<li>KIMCHIIIII!</li>

</ul>

<h3>30.8.</h3>

<div>

<ul>

	<li>Rice + soup + Kimchi = Korean breakfast. No, thanks, once was more than enough.</li>

	<li>No internet access for us yet. Sad sad situation. Thanks god for Kim's network.</li>

	<li>Orientation!</li>

	<li>Mobile phones everywhere. IM-ing or watching TV, everybody plays with his phone.</li>

	<li>Once you get used to their kind of beauty, Korean girls are pretty.</li>

	<li>Immigration office is a bureaucratic mess. Thanks god we had an appointment set by the uni.</li>

	<li>A/C everywhere. It's quite uncomfortable to change environments so often, because outside it's hot and humid and inside it's freezing.</li>

	<li>Lunch with the dean. Free food!</li>

	<li>Mentor-mentee meeting. My mentor absent, though. Took that opportunity to join the group with the pretties mentor around.</li>

</ul>

<h3>31.8.</h3>

<ul>

	<li>This uni has some cool spots at the campus.</li>

	<li>My registration for the school portal does not work.</li>

	<li>Korean culture demonstration. Trying on clothes and eating some sweets.</li>

	<li>Internet in the dorm. Amazing!</li>

	<li>Bud Bar in the evening. A 3L pitcher of Cass for 11,000 KRW (less than 6E). First late night return to the dorm. Welcome, exchange.</li>

</ul>

</div>

<h3>1.9.</h3>

<div>

<ul>

	<li>School starts. Well, no classes for me yet, but still...</li>

	<li>The portal registration still does not work for me.</li>

	<li>Party night in Hongdae. Dinner (very spicy), beers and then Cocoon club. Sweet dance moves, me being the second tallest guy around, our group dominating the stage (hell yeah!), coming back at 6AM.</li>

</ul>

</div>

<h3>2.9.</h3>

<div>

<ul>

	<li>Hangover.</li>

	<li>Still no portal access.</li>

</ul>

</div>

<h3>3.9.</h3>

<div>

<ul>

	<li>Being touristic — visiting the National Museum of Korea and taking zillions of photos.</li>

</ul>

<h3>4.9.</h3>

<div>

<ul>

	<li>Lazy sunday</li>

	<li>First time to the KAIST gym. It has several advantages - it is 24/7, it is close and it is for free. /me likes it.</li>

	<li>First week in Seoul is done. And it was awesome. Another 15 to go!</li>

</ul>

</div>

</div>
	\end{content}
\end{post}
