\begin{post}
	\postdata{Explanation}{2011}{9}{9}{13}{25}{57}
	\begin{content}
Just to make sure that everybody knows whats going on...

As you might know, I am doing my MSc. in The Netherlands, at the Delft University of Technology. Last year I found out that our faculty has several agreements with universities all around the world regarding exchange programs. Well, that naturally caught my attention so I started thinking about going further abroad for another semester. I have decided to go to Asia, because Europe does not make sense for me and I did not feel like going to the USA or another English-speaking country. Moreover, the Asian culture is so different from Europe that any experience with it might be very valuable. There were basically three choices — Harbin in China, Tokyo in Japan and Seoul in Korea. Because Harbin was only for two months and Japan is quite expensive and maybe a little too \sout{weird} different, I have decided to come to KAIST Business School in Seoul, which is a MBA oriented part of the otherwise technically oriented KAIST university in Daejeon.

The application and organization was a bit of a struggle, but luckily everything worked out fine and I was admitted to the Fall 2011 Exchange program. I am focusing mainly at Information and Media MBA, which is in line with my planned master thesis direction. I will spend 4 months here and then come back to Delft to start working on my master thesis. So, that's why I am here and not in Europe. Simple, right...
	\end{content}
\end{post}
